Manuscript results

### 2024-08-23 05_report/Manuscript_results_temp.Rmd
updated

```{r}
fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime investigator combo")
index <- c(1:30)
nn <- length(index)
```

@@

```{r}
# Averaging cohort traces across simulation run
l_prop_df <- list.files(paste0(fileloc, "/trace"),full.names = TRUE)[index]
prop_df  <- map_df(l_prop_df[1], readRDS) 
prop_df$cycle <- as.numeric(prop_df$cycle)
prop_df$intervention <- ifelse(prop_df$intervention == "Targeted", 1, 0)
prop_df <- apply(prop_df,2,as.numeric)
prop_df <- as.data.frame(prop_df)
prop_df <- prop_df %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
if (nn > 1) {
  for (i in 2:nn) {
    prop_df_i  <- map_df(l_prop_df[i], readRDS) 
    prop_df_i$cycle <- as.numeric(prop_df_i$cycle)
    prop_df_i$intervention <- ifelse(prop_df_i$intervention == "Targeted", 1, 0)
    prop_df_i <- prop_df_i %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
    prop_df_i <- apply(prop_df_i,2,as.numeric)
    prop_df_i <- as.data.frame(prop_df_i)
    prop_df <- prop_df + prop_df_i
  }
  prop_df <- prop_df/nn
}
prop_df$intervention <- ifelse(prop_df$intervention == 1, "Targeted", "SoC")

@@

>>>>

```{r}
fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime investigator combo")
index <- c(1:50)
nn <- length(index)
```

@@

```{r}
# Averaging cohort traces across simulation run
l_prop_df <- list.files(paste0(fileloc, "/trace"),full.names = TRUE)[index]
prop_df  <- map_df(l_prop_df[1], readRDS) 
prop_df$cycle <- as.numeric(prop_df$cycle)
prop_df$intervention <- ifelse(prop_df$intervention == "Targeted", 1, 0)
prop_df <- apply(prop_df,2,as.numeric)
prop_df <- as.data.frame(prop_df)
prop_df <- prop_df %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual",      
                                             "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
p_surv <- p_surv_plgg <- as.data.frame(matrix(NA,nrow=nrow(prop_df), ncol=nn))
p_surv$intervention  <- prop_df$intervention
p_surv_plgg$intervention <- prop_df$intervention
p_surv$cycle  <- prop_df$cycle
p_surv_plgg$cycle <- prop_df$cycle
p_surv[,1] <- 1 - (prop_df$death_outside + prop_df$death_cardio + prop_df$death_SN + prop_df$death_stroke +
                  prop_df$death_plgg)
p_surv_plgg[,1] <- 1 - prop_df$death_plgg

if (nn > 1) {
  for (i in 2:nn) {
    prop_df_i  <- map_df(l_prop_df[i], readRDS) 
    prop_df_i$cycle <- as.numeric(prop_df_i$cycle)
    prop_df_i$intervention <- ifelse(prop_df_i$intervention == "Targeted", 1, 0)
    prop_df_i <- prop_df_i %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
    prop_df_i <- apply(prop_df_i,2,as.numeric)
    prop_df_i <- as.data.frame(prop_df_i)
    prop_df <- prop_df + prop_df_i
    # calculate overall survival
    p_death_i <- prop_df_i$death_outside + prop_df_i$death_cardio + prop_df_i$death_SN + prop_df_i$death_stroke +
                  prop_df_i$death_plgg
    p_surv[,i] <- 1 - p_death_i
    # calculate plgg-related survival
    p_death_plgg_i <- prop_df_i$death_plgg
    p_surv_plgg[,i] <- 1 - p_death_plgg_i
  }
  prop_df <- prop_df/nn
}
prop_df$intervention <- ifelse(prop_df$intervention == 1, "Targeted", "SoC")

@@

```{r}
# Survival
## Overall
p_surv$intervention <- ifelse(p_surv$intervention == 1, "Targeted", "SoC")
p_surv1 <- data.frame(avg = apply(p_surv %>% select(-cycle, -intervention), 1, mean),
                      lb = apply(p_surv %>% select(-cycle, -intervention), 1, function(x){quantile(x, 0.025)}),
                      ub = apply(p_surv %>% select(-cycle, -intervention), 1, function(x){quantile(x, 0.975)}))
p_surv1$intervention <- p_surv$intervention
p_surv1$cycle <- p_surv$cycle/12
ggplot(p_surv1, aes(x = cycle)) +
  geom_ribbon(aes(ymin = lb, ymax = ub), fill = "blue", alpha = 0.2) +  
  geom_line(aes(y = avg), color = "blue") +  
  labs(x = "Time", y = "Survival Probability", 
       title = "Overall Survival Over Time with 95% Confidence Interval") +
  theme_bw() + facet_wrap(~intervention)

## PLGG
p_surv_plgg$intervention <- ifelse(p_surv_plgg$intervention == 1, "Targeted", "SoC")
p_surv_plgg1 <- data.frame(avg = apply(p_surv_plgg %>% select(-cycle, -intervention), 1, mean),
                      lb = apply(p_surv_plgg %>% 
                                   select(-cycle, -intervention), 1, function(x){quantile(x, 0.025)}),
                      ub = apply(p_surv_plgg %>% 
                                   select(-cycle, -intervention), 1, function(x){quantile(x, 0.975)}))
p_surv_plgg1$intervention <- p_surv_plgg$intervention
p_surv_plgg1$cycle <- p_surv_plgg$cycle/12
ggplot(p_surv_plgg1, aes(x = cycle)) +
  geom_ribbon(aes(ymin = lb, ymax = ub), fill = "blue", alpha = 0.2) +  
  geom_line(aes(y = avg), color = "blue") +  
  labs(x = "Time", y = "surv_plggival Probability", 
       title = "PLGG-related survival Over Time with 95% Confidence Interval") +
  theme_bw() + facet_wrap(~intervention)
```
